\section{Experience}

% \vspace{2pt}

%\begin{itemize}

    {\cventry{Jun 2026 -- Sep 2026}{Research Intern}{Microsoft Research}{}{}{%\vspace{3pt}
    \begin{itemize}
    \item Building efficient models and inference systems for compound and coordinated physical AI workloads.
    \end{itemize}
    }}

    {\cventry{Sep 2023 -- Present}{Graduate Research Assistant}{Computer Science Department, The University of Chicago}{}{}{%\vspace{3pt} 
    \begin{itemize}
    \item Quality-cost optimization for LLM Agentic Systems with unified agent memory and KV Cache management.
    \item Joint quality-latency optimization for Retrieval Augmented Generation (RAG) LLM systems with query-level configuration selection and memory management.
    \item Transformer based models for sharp latency change prediction to enable packet-level queue management and tail-latency reduction for latency-sensitive applications.
    \end{itemize}
    }}

    {\cventry{Jun 2025 -- Sep 2025}{Research Intern}{Microsoft Research}{}{}{%\vspace{3pt}
    \begin{itemize}
    \item Joint internship with Outlook for scalable and cost-efficient LM architectures for email importance labeling.
    \item Built a hybrid architecture with SLM cascades and embedding classifiers to reduce labeling COGS upto 150X, with negligible quality loss. Deployed in Outlook's production email client.
    \end{itemize}
    }}

    {\cventry{Sep 2022 -- Mar 2023}{Cloud Networks Researcher}{Advanced Network Architectures Lab, UPC Barcelona}{}{}{%\vspace{3pt} 
    \begin{itemize} 
    \item Developed an approximation for a Mixed-Integer Optimal Matching Algorithm for edge resource allocation to reduce execution time by 2.5-3X.
    \end{itemize}
    }}

    {\cventry{Oct 2021 -- Sep 2022}{Graduate Research Assistant}{Law, Economics, and Data Science Group, ETH Zurich}{}{}{%\vspace{3pt} 
    \begin{itemize}
    \item Improved semantic labeling pipelines for sentence simplification, paraphrase mining, and topic clustering.
    \item Developed NLP models to automatically analyse discourse in policy documents for actor-narrative clustering.
    \end{itemize}
    }}

%\vspace{4pt}

    {\cventry{May 2019 -- July 2019}{Software Development Intern}{Capgemini Engineering}{}{}{%\vspace{3pt} 
    \begin{itemize}
    \item Developed a K-Shortest Path Searching algorithm in an ONOS based Software Defined Layer 2 VPN.
    \item Algorithm applied dynamic constraints of network resources (e.g.required edges) for path calculation.
    \end{itemize}
    }}

%\vspace{4pt}

    {\cventry{May 2018 -- July 2018}{Software Development Intern}{BlueStacks}{}{}{%\vspace{3pt}
    \begin{itemize}
    \item  Developed an ML algorithm to customize the Bluestack's display screen using past users' experiences.
    \item  Built an automation tool to create SVG cards and an address verification tool for Bluestack's game engine.
    \end{itemize}
    }}

%\end{itemize}